Adaptive Approximation for Multivariate Linear Problems \\ with Inputs Lying in a Cone

### 2018-11-08 RICAM2018NovTalk.tex
polishing

\centerline{
    \begin{tabular}{>{\vspace{-1.7ex}\raggedleft}p{0.2\textwidth}@{\qquad}p{0.3\textwidth}@{\qquad}p{0.3\textwidth}}
    & \alert{Previous talks} & \alert{My reponse} \tabularnewline
    \toprule
    \alert{Henryk, Klaus, Greg, Stefan, \ldots} & Many results for $f \in \smallscoop$  &
    May we obtain analogous results for $f \in \smallcone$? \tabularnewline[2ex]
    \alert{Houman} & Let's \alert{learn} the appropriate kernel from the function data & Will only work for nice functions in a \smallcone \tabularnewline[2ex]
    \alert{Paul} & Let's \alert{find} the Lipschitz matrix constant \ldots & Yes, lets learn from the function data \tabularnewline[2ex]
    \alert{Klaus} & This adaptive algorithm has \alert{no theory}  & We want to construct adaptive algorithms \alert{with theory} \tabularnewline[2ex]
    \alert{Henryk} & Tractability & Yes! \tabularnewline[2ex]
    \alert{Greg} & POD weights & Yes!
    \end{tabular}}
\end{frame}

@@

\vspace{-1ex}
where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{linear functionals}, $\LambdaAll$, e.g.,

@@

\vspace{-1ex}
where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{linear functionals}, $\LambdaAll$
&

@@

\medskip

\alert{Construction}: Identify $\app \in \ca(\cc,\Lambda)$}

\medskip

@@

 \medskip

@@

\medskip

@@

@@

    \item Philosophy:  \alert{What we cannot observe is not much worse than what we can observe}

@@

\begin{frame}[label = BallsWontHelp]{``But I Like Balls \smallscoop!''}

\vspace{-5ex}
How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \alert{balls}?

@@

Three scenarios presented

@@

\begin{align*}
    f &= \sum_{\vj \in \cn} \hf(\vj) u_{\vj}, \qquad
    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}\\
    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
    \end{array}
    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
\end{align*}

>>>>

\centerline{
    \begin{tabular}{>{\vspace{-1.7ex}\raggedleft}p{0.2\textwidth}@{\qquad}p{0.33\textwidth}@{\qquad}p{0.27\textwidth}}
    & \alert{Tidbits from talks this week} & \alert{My reponse} \tabularnewline
    \toprule
    \alert{Henryk, Klaus, Greg, Stefan, Erich, \ldots} & Many results for $f \in \smallscoop$  &
    Let's obtain analogous results for $f \in \smallcone$? \tabularnewline[2ex]
    \alert{Houman} & Let's \alert{learn} the appropriate kernel from the function data & Will only work for nice functions in a \smallcone \tabularnewline[2ex]
    \alert{Klaus} & ``This adaptive algorithm has \alert{no theory}''  & We want to construct adaptive algorithms \alert{with theory} \tabularnewline[2ex]
    \alert{Henryk} & Tractability & Yes! \tabularnewline[2ex]
    \alert{Greg} & POD weights & Yes! \tabularnewline[2ex]
    \alert{Mac} & Function values are expensive & Yes!
    \end{tabular}}
\end{frame}

@@

\vspace{-1ex}
where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{any linear functionals}, $\LambdaAll$, e.g.,

@@

\vspace{-1ex}
where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{any linear functionals}, $\LambdaAll$
&

@@

\smallskip

\alert{Construction}: Find $\app \in \ca(\cc,\Lambda)$}

\smallskip

@@

 \smallskip

@@

@@

\smallskip
\uncover<4->{\alert{Implementation} in open source software}

@@

    \item \alert{Philosophy:}  What we cannot observe about $f$ is not much worse than what we can observe about $f$

@@

\begin{frame}[label = BallsWontHelp]{``But I Like \smallscoop!''}

\vspace{-5ex}
How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \smallscoop?

@@

Three scenarios presented here:

@@

\begin{align*}
    S(f) & = \int_{[0,1]^d} f(\vx) \, \dif \vx\\[2ex]
    f &= \sum_{\vj \in \cn} \hf(\vj) u_{\vj}, \qquad
    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \delta_{\vj,\vzero}\\
    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
    \end{array}
    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
\end{align*}
